\Large \bf \projtitle

### 2015-05-06 doc/paper/paper.tex
Fix bug
added signaling channel description

\inclfigure{fig:components}{components.eps}{
    Relationship between different client-side components of the \zbf\
    peer-to-peer download service. Components in gray are standard browser
    APIs.
}

@@

The signaling channel enables
% katie

>>>>

\inclfigure{fig:components}{components.pdf}{
    Relationship between different client-side components of the \zbf\
    peer-to-peer download service. Components in gray are standard browser
    APIs.
}

@@

The signaling channel facilitates opening the WebRTC data channel connection between
peers. The WebRTC protocol requires one peer to send a WebRTC offer and ICE candidate
to the other peer, and that other peer to send back a WebRTC answer, for a peer-to-peer
data channel to be opened. The server-side signaling channel facilitates this
information transfer between peers by  directing offers, ICE candidates, and answers
to their specified peer recipient.
